### 2016-06-17 Manuscript/SW_early_life_telomeres.Rmd
More edits

###Results
We measured telomere lengths using a total of `r nrow(dd)` unique samples from juvenile and adult Seychelles warblers. Of these, `r nrow(juv)` samples were taken cross-sectionally from birds caught within their first year of life, and of these juvenile birds, we had additional longitudinal samples for `r nrow(Loss)`. Efficiencies (mean $\pm$ s.d.) for our telomere and GAPDH reactions were (`r round2(mean(dd$EffTelomere))` $\pm$ `r round2(sd(dd$EffTelomere))`) and (`r round2(mean(dd$EffGAPDH))` $\pm$ `r round2(sd(dd$EffGAPDH))`) respectively. Inter-plate repeatability of RTL, based on `r nrow(subset(ddL,Group == 'Within samples'))` samples measured at least twice, was 0.78 (CI = 0.73-0.82).

>>>>

###Results
We measured telomere lengths using a total of `r nrow(dd)` unique samples from juvenile and adult Seychelles warblers. Of these, `r length(unique(subset(dd,Agemonths<12)$BirdID))` samples were taken cross-sectionally from birds caught within their first year of life. Efficiencies (mean $\pm$ s.d.) for our telomere and GAPDH reactions were (`r round2(mean(dd$EffTelomere))` $\pm$ `r round2(sd(dd$EffTelomere))`) and (`r round2(mean(dd$EffGAPDH))` $\pm$ `r round2(sd(dd$EffGAPDH))`) respectively. Inter-plate repeatability of RTL, based on `r nrow(subset(ddL,Group == 'Within samples'))` samples measured at least twice, was 0.78 (CI = 0.73-0.82).

### 2016-06-17 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
More edits

temp <- subset(dd,!is.na(cenTQ))
temp$LogAge <- log(temp$Agemonths)

#Run the model
lm2 <- lmer(RTL ~  LogAge* (Tarsus + NonHelper + Sex + BodyMass  + cenTQ)  + (1|FieldPeriodID) + (1|BirdID) + (1|TerritoryID),
            data = temp,
            REML = FALSE)
lm2 <- standardize(lm2)
#Model averaging

@@

temp <- with(dd3,tapply(DeltaRTL,Agemonths,mean))
tempSE <- with(dd3,tapply(DeltaRTL,Agemonths,se))*1.96

plot(temp~names(temp),type = 'l',ylim = c(-0.8,0.8))
points(temp+tempSE~names(temp),type = 'l',lty = 2)
points(temp-tempSE~names(temp),type = 'l',lty = 2)
abline(0,0,col = 'red',lwd = 2)

plot(DeltaRTL~TimeDiff,data = dd3)

>>>>

temp <- juv_r
temp$LogAge <- log(temp$Agemonths)

#Run the model
lm2 <- lmer(RTL ~  LogAge* (Helper)+Tarsus + NonHelper + Sex + BodyMass  +yday*LogAge + (1|FieldPeriodID) + (1|BirdID) + (1|TerritoryID),
            data = temp,
            REML = FALSE)
lm2 <- standardize(lm2)
#Model averaging

@@
